Untitled

### 2020-09-14 Rmd/brms_metric_selfing.Rmd
edits

# Model 2

@@

@@

>>>>

# Model 2 Excluding species with flowers with separated sexes

@@

Again, the fit seems right, check now estimates, se and credible intervals:

@@

Logit estimates, credible intervals and points

#Log
ggplot(data=p1.1[[1]], aes(x = autonomous_selfing_level, y = log(visits),color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1.1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=log(lower__), ymax=log(upper__)), width=.1, color="black")+
  geom_point(data=p1.1[[1]], mapping=aes(x=autonomous_selfing_level, y=log(estimate__)), color="black") + ylab("Visits") + xlab("Selfing level")+
  theme(legend.position = "none")

Including or excluding dioecious and monoecious species does not make a very big differences in the models.

BAYES R2 Model 1 including all species

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)
setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1.1_visits_self_all.RData")
load("Data/RData/brms_m1_visits_self_all.RData")

bayes_R2(m1)
p1[[1]]
```

BAYES R2 Model 1 without monoecious and dioecious species

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)
setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1.1_visits_self_all.RData")
load("Data/RData/brms_m1_visits_self_all.RData")
bayes_R2(m1.1)
p1.1[[1]]

Because the qualitative data can add some noise to the analysis now I'm going to exclude it and just consider species that have quantitative information of the auntonomous selfing level.

#MODEL 3 JUST QUANTITATIVE DATA BUT GROUPED IN 4 CATEGORIES NONE, LOW, MEDIUM, HIGH.

Two distributions fit the data: **Negative binomial** and **skew gaussian** with logit transformation of visits and because for the negative binomial I have to to log transform the data in order to improve visualization. I'm going to keep from now on with a **skew gaussian** with the logit of visits (the output is quite similar).

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(brms)
library(ggplot2)
library(tidybayes)
library(tidyverse)
library(kableExtra)
setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1.2.1_visits_self_all.RData")
load("Data/RData/brms_data_m1.2.1_visits_self_all.RData")

c_e.1.2.1 <- conditional_effects(m1.2.1)
p1.2.1 <- plot(c_e.1.2.1, points=T,plot = FALSE)[[1]]

ggplot(data=p1.2.1[[1]], aes(x = autonomous_selfing_level, y = log(visits),color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_4,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1.2.1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p1.2.1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
  theme(legend.position = "none")

bayes_R2(m1.2.1)

p1.2.1[[1]]
